---
title: "Intro to Interactive Slide Decks | Xaringan"
author: "Ezekiel Adebayo Ogundepo"
institute: "Data Science Nigeria"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: [default,  "rladies", "rladies-fonts"]
    lib_dir: libs
    nature:
      highlightStyle: arta
      highlightLines: true
      countIncrementalSlides: false
---


```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)

knitr::opts_chunk$set(echo = TRUE, 
                      tidy = 'styler', 
                      comment = NA,
                      message = FALSE,
                      warning = FALSE)

```


```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_duo_accent(
  primary_color = "#1381B0",
  secondary_color = "#FF961C",
  inverse_header_color = "#FFFFFF"
)

# Loaded packages

install.load::install_load(c("knitr", "xaringanExtra", "xaringan", "tidyverse", "kableExtra"))

# Use some functions in xaringanExtra

use_tile_view()

use_panelset()

use_webcam(width = 150, height = 150)

use_clipboard()

use_editable()

use_animate_all("fade")

use_broadcast()

```
class: center, middle

```{r, echo=FALSE}
knitr::include_graphics("https://upload.wikimedia.org/wikipedia/commons/b/be/Sharingan_triple.svg")
```

## xaringan

### /ʃæ.'riŋ.ɡæn/


---
class: inverse, center, middle

# Get Started

---

# Hello World

Install the **xaringan** package from [Github](https://github.com/yihui/xaringan):

```{r eval=FALSE, tidy=FALSE}
devtools::install_github("yihui/xaringan")
```



--

You are recommended to use the [RStudio IDE](https://www.rstudio.com/products/rstudio/), but you do not have to.

- Create a new R Markdown document from the menu `File -> New File -> R Markdown -> From Template -> Ninja Presentation`

--

- Click the `Knit` button to compile it;

--

- or use the [RStudio Addin](https://rstudio.github.io/rstudioaddins/)<sup>2</sup> "Infinite Moon Reader" to live preview the slides (every time you update and save the Rmd document, the slides will be automatically reloaded in RStudio Viewer.


---

# Awesome Title

Here is some text. 

- Bullet 1
- Bullet 2

``` r
code <- "awesome"
```

And don't forget to set up __Infinite Moon Reader RStudio Addin!__

---
# New Slide

This is a simple introduction to Xaringan. This is my beloved brother

---
class: top, center

#  Top Center

More stuff

.left[I love you]

.right[I love you the more ...]

---
# Incremental Reveals

--

item 1

--

Item 2

--

One final piece

---

# Two-Columns

.pull-left[

- Hello

- how

- are

- you

- ?
]

.pull-right[

I love you
]

---

# Code Highlight & Tables

```{r, echo=T}
iris %>%
  knitr::kable()
```

---

# DT Tables

```{r, echo=FALSE}
library(DT)

iris %>% DT::datatable()
```

---

# Maps

```{r, out.width="100%", warning=F}
library(leaflet)

leaflet() %>%
  setView(lng = -71.0589, lat = 42.3601, zoom = 12) %>%
  addProviderTiles(providers$Esri.NatGeoWorldMap)
```

---

# Plots

```{r, out.width="100%", out.height="70%"}
library(timetk)

m4_monthly %>%
  plot_time_series(date, value, .facet_vars = id, .facet_ncol = 2)
```

---
# Side-by-Side

.pull-left[

Let's check out the monthly seasonality. 

```{r}
library(timetk)

p <- m4_monthly %>%
  filter(id == "M750") %>%
  plot_time_series(
    .date_var   = date, 
    .value      = value
  )
```

]

.pull-right[
```{r, echo=F, out.width="100%"}
p
```


]

---

# Themes

```{r}
names(xaringan:::list_css())
```



---

# Lot's more!

- [_"Meet xaringan"_: Allison Hill's RStudio 2019 Conf Talk](https://arm.rbind.io/slides/xaringan.html)

- [_"Applying design guidelines to slides with {xaringanthemer}"_: By Katie Jolly](https://www.katiejolly.io/blog/2021-03-16/designing-slides)

- [_"Presentation Ninja with xaringan"_ by Yihui Xie](https://slides.yihui.org/xaringan/#1)

.center[
  ![](https://upload.wikimedia.org/wikipedia/commons/b/be/Sharingan_triple.svg)
]



